RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-12 paper.tex
knitr cite
update

@@

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to 
  share their findings and to move results from exploratory data analysis
  to automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams could greatly benefit from easier sharing of
  scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide.  In this paper, we propose RCloud, a system that supports
  collaborative data analysis, visualization and web deployment. We will
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
} % end of abstract

@@

"Coordination is done by meetings"

"how do you trace an automated alert back to an EDA environment ?"

@@

@@

@@

@@

>>>>

% DevOps for Visual Analysis and Data Science

@@

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to 
  share their findings and to move results from exploratory data analysis
  to automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams could greatly benefit from easier sharing of
  scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide.  \todo{sell idea, not system} In this paper, we propose RCloud, a system that supports
  collaborative data analysis, visualization and web deployment. We will
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
} % end of abstract

@@

@@

\todo{Points we want to make."Coordination is done by meetings" "how do you trace an automated alert back to an EDA environment ?"}

% What's the area
Consider the emerging role of a data science team within an
organization.

% How do people do it today?
Individual data scientists and statisticians usually
work on loosely related problems, and must devise effective ways to 
share their findings and to move results from exploratory data analysis
to automated diagnostics and reports deployed for wider consumption.

% Why does this not work?
There are two problems with the current
practice. First, there are gaps in this workflow: EDA is performed
with one set of tools, and automated reports and deployments with another.
Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from easier sharing of
scripts and data feeds, experiments, annotations, and automated
recommendations, which are well beyond what traditional version control
systems provide.

% What are we going to do about this?
\todo{Sell idea, not system} In this paper, we propose RCloud, a system that supports
collaborative data analysis, visualization and web deployment. We will
discuss the design decisions, tradeoffs and limitations, and compare RCloud
to other current proposals.

% What is the scope of our solution?

% We want our solution to play well with the rest of the ecosystem

@@

Design for cloud-friendly? This goes back to the point in the
introduction about playing nice with the rest of the ecosystem.

@@

\subsection{Technologies: R, Python, HTML5, interactive notebooks, etc.}

How do we do things that are not trivial to do with IPython (for example)

dcplot. two-way communication between between backend session and
frontend session.

@@

What are the decisions and ideas that are central to this paper?
